The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-24 paper/ms.tex
stuff

The dominant source of residual systematic errors in nominal \kepler time series is a common-mode variation primarily due to thermal changes on board the spacecraft, an issue which is traditionally dealt with by identifying and fitting a linear combination of systematic modes \citep{pdc0,pdc1,pdc2,petigura}. We adopt the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of  either the first~4 or~8 CBVs to each light curve. We note that this can subtract astrophysical signals on long timescales, such that we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, but otherwise use the 8~CBV light curves. There is some room for improvement here by simultaneously modelling astrophysical and instrumental variations, but this is beyond the scope of this paper. In the following, we will use the light curves with the lowest 6.5~hr Combined Differential Photometric Precision (CDPP) \citep{cdpp} out of all apertures, as calculated with the \textsc{k2sc} implementation \citep{k2sc}. \textcolor{red}{This is primitive - how do we justify this? We only did it because we didn't have anything cleverer, but now we do. Should I redo this?}. 
\subsection{Asteroseismology}
\label{asteroseismology}

For all \textcolor{red}{N} red giants identified in this sample, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$. These constrain fundamental stellar parameters independently from spectroscopic or interferometric measurements:

\begin{equation}
\numax \propto \dfrac{g}{g_{\sun}} \cdot \dfrac{\teff}{\teff_{\sun}}^{\dfrac{1}{2}}
\end{equation}

@@

\section{Asteroseismology}
\label{asteroseismology}

@@

@@

>>>>

The dominant source of residual systematic errors in nominal \kepler time series is a common-mode variation primarily due to thermal changes on board the spacecraft, an issue which is traditionally dealt with by identifying and fitting a linear combination of systematic modes \citep{pdc0,pdc1,pdc2,petigura}. We adopt the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of  either the first~4 or~8 CBVs to each light curve. We note that this can subtract astrophysical signals on long timescales, such that we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, but otherwise use the 8~CBV light curves. There is some room for improvement here by simultaneously modelling astrophysical and instrumental variations, but this is beyond the scope of this paper. In the following, we will use the light curves with the lowest 6.5~hr Combined Differential Photometric Precision (CDPP) \citep{cdpp} out of all apertures, as calculated with the \textsc{k2sc} implementation \citep{k2sc}. \textcolor{red}{This is primitive - how do we justify this? We only did it because we didn't have anything cleverer, but now we do. Should I redo this?}.

\subsection{Asteroseismology}
\label{asteroseismology}

For all \textcolor{red}{N} red giants identified in this sample, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters independently from spectroscopic or interferometric measurements:

\begin{equation}
\label{scaling}
\numax \propto \dfrac{g}{g_{\sun}} \cdot \dfrac{\teff}{\teff_{\sun}}^{\dfrac{1}{2}}
\end{equation}

@@

Once \numax has been estimated, we use the asteroseismic scaling relation for \numax \citep[Equation~\ref{scaling};][]{KB95} to estimate \logg in order to inform extraction of chemical abundances from spectra. Using the initial spectroscopic estimate of \Teff, which is not significantly informed by \numax, we propagate uncertainties in \numax with Monte Carlo sampling.

@@

\textcolor{red}{Keith - can you describe how you got the abundances here?}

@@

\textcolor{red}{Ashley/Dan/Vichi?}
